\documentclass{ExpressiveCoverLetter}

\begin{document}

\vspace{0.25in}
1809 Lakebend Dr \newline
Sugar Land, TX 77478 \newline
July 9, 2024

\vspace{0.15in}

Ms. Monique Brady \newline
Early Career Recruiting, Apple \newline
One Apple Park Way \newline
Cupertino, CA 95014 \newline

Dear Ms. Brady, \newline

I was encouraged to contact you after meeting your colleague Mr. Cook at
the TAMUhack event last week. I am writing to express my enthusiasm for
the Machine Learning / AI Internship within Apple’s AIML organization.
As a Computer Science student specializing in Deep Learning and an avid
Apple fan, I am excited about the opportunity to contribute to Apple’s future developments. My
hands-on project experience and technical background position me well to
help Apple innovate unprecedented technologies that continue to change
the world. \newline

During my internship at Albedo, I transformed and preprocessed the COWC
dataset of 13K aerial images to enhance image classification accuracy.
Using scikit-learn and OpenCV, I converted annotations to YOLOv4 format,
addressed data quality issues, and created balanced train/test splits.
By iteratively fine-tuning the YOLOv4 model, I achieved a 93\% mAP in
classifying various automobiles in aerial satellite imagery and
demonstrated the decrease in performance with downsampled imagery at
different levels. Independently mastering complex tasks without prior
experience, I delivered valuable results and am eager to bring this
ability to tackle challenges and achieve impactful outcomes to Apple's
innovative projects. \newline

In another project, I developed a Tennis Ball Tracking and Court Line
Detection System leveraging knowledge from DeepLearning.AI's TensorFlow
Developer course and Deep Learning Specialization. Using YOLO models
with PyTorch, I achieved 90\% mAP in object detection and tracking,
meeting the metrics necessary for real-time mobile tennis analysis. This
project demonstrates my ability to manage end-to-end development and
apply machine learning techniques to solve real-world problems, aligning
with Apple's goal of delivering innovative products through
problem-solving and experimentation. \newline

Apple provides its employees unparalleled opportunities to innovate with the brightest minds, us- ing high-quality resources, and impacting millions of users worldwide. I look forward to discussing how my skills and experiences can contribute to Apple’s AIML team. I have attached my resume, and feel free to contact me at (832) 491-4811 or ry4ntr1@gmail.com. I appreciate your time and consideration and look forward to hearing from you soon.\newline

Sincerely, \newline

Ryan Tri \newline

\end{document}
