\documentclass{ExpressiveResume}

% ----- Resume -----
\begin{document}

% ----- Name + Contact Information -----
\resumeheader[
firstname=Ryan,
lastname=Tri,
email=ry4ntr1@gmail.com,
phone=832-491-4811,
linkedin=ry4ntr1,
github=ry4ntr1,
city=Sugar Land,
state=Texas,
qrcode=./images/qr.png,
fixobjectivespacing=true
]

\objective{Undergraduate Computer Science student at Texas A\&M University with an interest in Deep Learning applications for sports analysis systems, wearable health technology, neurobiology, and multimodal environments.}

% ----- Education -----
\section{Education}

\education{Computer Science}{Bachelor of Science}{May 2025}{
\noindent Texas A\&M University \newline
\noindent GPA: 3.904/4.0 \newline
College Station, Texas \newline \newline
\noindent \textbf{Relevant Coursework:} Data Structures and Algorithms, Discrete Structures for Computing, Linear Algebra, Statistics, Computer Organization, Design and Analysis of Algorithms, Foundations of Software Engineering, Principles of Data Science, Machine Learning, Artificial Intelligence
}

% ----- Work Experience -----
\section{Experience}

\experience{Software Engineering Intern}{Albedo}{Jun 2021}{Aug 2021}{
    \achievement{Preprocessed 13K aerial images from the COWC dataset using \textbf{scikit-learn} and \textbf{OpenCV}.}
    \achievement{Converted annotations to \textbf{YOLOv4} format, addressed data quality issues, and created balanced train/test splits.}
    \achievement{Implemented and fine-tuned the \textbf{YOLOv4} model on \textbf{Google Colab} using \textbf{Darknet}, achieving a 95\% mAP.}
    \achievement{Optimized hyperparameters to improve detection accuracy and reduce false positives by 20\%.}
    \achievement{Presented findings to upper management, influencing strategic decisions for future AI model enhancements.}
}


% ----- Technical Projects -----
\section{Projects}

\experience{Mess Waffles POS System}{Texas A\&M University}{Sep 2023}{Dec 2023}{
\achievement{Developed a POS system for Mess Waffles, improving efficiency and data analytics.}
\achievement{Designed user interfaces using \textbf{TypeScript}, \textbf{Vite}, and \textbf{Material-UI}, enhancing user experience.}
\achievement{Implemented secure \textbf{OAuth2.0} authentication and integrated \textbf{Google Maps}, \textbf{Weather}, and \textbf{Translate} APIs with \textbf{Express.js} and \textbf{PostgreSQL} for seamless interactions.}
\achievement{Developed real-time order processing and inventory management, reducing restock losses by 15\% through timely notifications and data-driven analytics.}
\achievement{Deployed on \textbf{AWS EC2} with CI/CD pipelines using \textbf{GitHub Actions}, ensuring efficient updates.}
}

\experience{Tennis Ball Tracking and Court Line Detection System}{Personal Project}{Jan 2024}{Jul 2024}{
\overview{\noindent Developed a system for tracking tennis balls and detecting court lines using machine learning and computer vision.}
\achievement{Implemented ball tracking with \textbf{YOLO} models using \textbf{PyTorch} and \textbf{Ultralytics}, achieving 90\% detection accuracy.}
\achievement{Trained custom models and developed court line detection with \textbf{OpenCV}, improving detection performance by 25\% and accuracy by 10\%.}
\achievement{Processed videos with \textbf{pandas} and \textbf{numpy}, conducting model training with data augmentation and hyperparameter tuning, optimizing performance and enabling real-time inference with 20\% reduced latency.}
\achievement{Created utility scripts for bounding box operations and video processing, enhancing system functionality and maintainability.}
}

% ----- Skills -----
\section{Skills}

\skill{\noindent \textbf{Programming Languages:} Python, C++, Java, TypeScript, SQL, JavaScript, Swift} \newline
\skill{\noindent \textbf{Machine Learning Frameworks:} TensorFlow, PyTorch, scikit-learn, Keras, YOLO} \newline
\skill{\noindent \textbf{Data Processing and Analysis:} Pandas, Numpy, Matplotlib, OpenCV} \newline
\skill{\noindent \textbf{Cloud Platforms:} AWS (Amazon Web Services), Google Cloud Platform (GCP)} \newline
\skill{\noindent \textbf{Tools, Technologies, and Methodologies:}
    Docker, Git, React, Node.js, Flask, PostgreSQL, Agile, Vite} \newline

% ----- Certifications -----
\section{Certifications}
\achievement{TensorFlow Developer, DeepLearning.AI, May 2023}
\achievement{Convolutional Neural Networks in TensorFlow, DeepLearning.AI, May 2023}
\achievement{Natural Language Processing in TensorFlow, DeepLearning.AI, May 2023}
\achievement{Improving Deep Neural Networks: Hyperparameter Tuning, Regularization and Optimization, DeepLearning.AI, Jun 2021}
\achievement{Structuring Machine Learning Projects, DeepLearning.AI, Jun 2021}

\end{document}
